MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)

### 2014-10-06 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\section{Experiments}\label{s:experiments}
We have implemented MLISA in Java\footnote{Source code of implementation available at: https://github.com/Marooned202/MLISA}. We have extracted the set of features for 4532 web services in 64 different time slots, through a data set provided by \cite{10.1109/ISSRE.2011.17}. By choosing 86 web services out of these set, and choosing a subset of set of all possible combinations of size 2,3,4 of these 86 web services, we have chosen 10,000 communities and evaluated the feature vectors and utilities they can have in 64 different time slots. This provides us with the initial training feature set of size $|CFVS| = 10,000$ communities. \footnote {The template vector and gain matrix generated are available online at http://todo"}

>>>>

\section{Experiments}\label{s:experiments}
We have implemented MLISA in Java\footnote{Source code of implementation and data is available at: \emph{https://github.com/Marooned202/MLISA}}. We have extracted the set of features for 4532 web services in 64 different time slots, through a data set provided by \cite{10.1109/ISSRE.2011.17}. By choosing 86 web services out of these set, and choosing a subset of set of all possible combinations of size 2,3,4 of these 86 web services, we have chosen 10,000 communities and evaluated the feature vectors and utilities they can have in 64 different time slots. This provides us with the initial training feature set of size $|CFVS| = 10,000$ communities\footnote {The template vector and gain matrix generated are available at \emph{https://github.com/Marooned202/MLISA/tree/master/wsds/data/run}}.
